---
title: "analysis"
author: "Mengyun Yang"
date: "`r Sys.Date()`"
output: 
  bookdown::html_document2
bibliography: references.bib
link-citations: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      warning = FALSE,
                      message = FALSE,
                      fig.align = "center")

options(scipen = 999)
```

```{r}
library(tidyverse)
library(dplyr)
library(glue)
library(ggplot2)
library(here)
library(readxl)
library(stringr)
library(scales)
library(forcats)
library(plotly)
library(tmap)
library(sf)
library(leaflet)
library(shiny)
library(ggthemes)
library(kableExtra)
library(gt)
library(ggpubr)
```


```{r}
# data from world bank
pop <- read.csv(here("data/population_data.csv"))
```


# Population
## Female population VS male population over the years

```{r, eval = FALSE}
# cleaning 
names(pop) <- tolower(names(pop))

pop_tidy <- pop %>% 
  select("series.name",
         "country.name",
         "country.code",
         5:14) %>% 
  pivot_longer(cols = 4:13,
               names_to = "year",
               values_to = "population") %>% 
  rename(sex = "series.name") %>% 
  mutate(sex = str_remove(sex, "Population,[:blank:]"),
         year = str_remove(year, "x[0-9]+..yr"),
         year = str_remove(year, "\\.$"),
         year = str_trim(year, side = "right"),
         population = as.numeric(population))
  

```

```{r, eval = FALSE}
# plot it

pop_tidy$tooltip <- 
  glue_data(pop_tidy,
            "Sex: {sex}",
            "\nYear: {year}",
            "\nPopulation: {comma(population, accuracy = 1)}")


ggplotly(
  
  pop_tidy %>% 
  filter(country.name == "World") %>% 
  ggplot(aes(x = year,
             y = population,
             group = sex,
             color = sex)) +
    geom_line(aes(text = tooltip)) +
    scale_y_continuous(labels = comma) +
    scale_color_brewer(palette = "Set1") +
    theme_light() +
    # theme(panel.grid.major.x = element_blank()) +
    labs(x = NULL,
         title = "Population by sex and year",
         caption = "Source: World Bank"),
  tooltip = "text"
    
    
  
) %>% 
  config(displayModeBar = FALSE,
         displaylogo = FALSE) 
  
```

## Population by sex and age

```{r}
# data from united nations, spreadsheet contains global and regional data by sex and age https://population.un.org/wpp/DataQuery/
pop_age <- read_excel(here("data/PopulationAgeSex-20211213064029.xlsx"), sheet = 2, range = "B2:Z17")
```

```{r, eval = FALSE}
# cleaning
names(pop_age) <- tolower(names(pop_age))

pop_age_long <- 
  pop_age %>% 
  pivot_longer(cols = 5:25,
               names_to = "age",
               values_to = "population")


# make male population go to the left of x axis, thus negative sign
pop_age_long$population <- ifelse(pop_age_long$sex == "Male", -1*pop_age_long$population, pop_age_long$population)
```

```{r, eval = FALSE}
# plot it
pop_age_long_20 <- pop_age_long %>% 
  filter(sex %in% c("Female", "Male"),
         time == "2020")

pop_age_long_20$tooltip <- 
  glue_data(pop_age_long_20,
            "Sex: {sex}",
            "\nPopulation (thousands): {ifelse(pop_age_long_20$sex == 'Male', comma(-(population), accuracy = 1), comma(population, accuracy = 1))}")



ggplotly(
  
pop_age_long_20 %>% 
  ggplot(aes(x = fct_inorder(age), # maintain order of age
             y = population,
             fill = sex)) +
  geom_bar(data = subset(pop_age_long_20, sex == "Female"), 
           aes(text = tooltip),
           stat = "identity") +
  geom_bar(data = subset(pop_age_long_20, sex == "Male"),
           aes(text = tooltip),
           stat = "identity") +
  scale_y_continuous(breaks = seq(-400000, 400000, 100000),
                     labels = paste0(as.character(c(seq(400, 0, -100), seq(100, 400, 100))), "m")) +
  coord_flip() +
  scale_fill_brewer(palette = "Set1") +
  theme_light() +
  labs(x = "Age",
       y = "Population",
       fill = "Sex"),
tooltip = "text"

) %>% 
  layout(title = list(text = paste0("Population by sex and age",
                                    "<br>",
                                    "<sup>",
                                    "Year: 2020",
                                    "</sup>"),
                      font = list(size = 12)),
         annotations = list(x = 0.1, 
                            y = -0.1, 
                            text = "Source: United Nations",
                            showarrow = FALSE, 
                            xref = "paper", 
                            yref = "paper",
                            xanchor = "right", 
                            yanchor = "auto", 
                            xshift = 0, 
                            yshift = 0,
                            font = list(size = 8)
)) %>% 
  config(displayModeBar = FALSE,
         displaylogo = FALSE) 

```

# Work
## Labour force

```{r}
labor <- read_excel(here("data/labor_force_world_bank.xlsx"))
```


```{r}
# cleaning 
names(labor) <- tolower(names(labor))

names(labor) <- gsub(" ", "_", names(labor))

labor_tidy <- labor %>% 
  select(-c(series_code, `2020_[yr2020]`)) %>% 
  pivot_longer(cols = 4:33,
               names_to = "year",
               values_to = "percentage") %>% 
  mutate(percentage = as.numeric(percentage),
         year = str_remove(year, "_\\[yr[0-9]+\\]")) 
```

```{r, eval = FALSE}
# plot it
labor_tidy_world <- labor_tidy %>% 
  filter(country_name == "World",
         series_name == "Labor force, female (% of total labor force)")


labor_tidy_world$tooltip <- 
  glue_data(labor_tidy_world,
            "Year: {year}",
            "\nPercentage: {paste(round(percentage, 2), '%', sep = '')}")


ggplotly(
  
labor_tidy_world %>% 
  ggplot(aes(x = year,
             y = percentage,
             group = 1)) +
  geom_line(aes(text = tooltip),
            color = "red") +
  geom_point(aes(text = tooltip),
             color = "red",
             size = 0.7) +
  theme_light() +
  theme(axis.text.x = element_text(angle = 90, size = 6),
        panel.grid.major.x = element_blank()) +
  labs(x = NULL,
       y = "Percentage %",
       title = "Female labor force percentage by year"),
tooltip = "text"

) %>% 
    layout(annotations = list(x = 0.1, 
                              y = -0.12, 
                              text = "Source: United Nations",
                              showarrow = FALSE, 
                              xref = "paper", 
                              yref = "paper",
                              xanchor = "right", 
                              yanchor = "auto", 
                              xshift = 0, 
                              yshift = 0,
                              font = list(size = 8)
)) %>% 
  config(displayModeBar = FALSE,
         displaylogo = FALSE) 
```

```{r}
# get world map and coordinates for each countries
data("World")

coords <- World %>% 
  select("iso_a3",
         "name",
         "geometry") %>% 
  rename(country_code = "iso_a3")

labor_tidy_coords <- labor_tidy %>% 
  filter(series_name == "Labor force, female (% of total labor force)") %>% 
  right_join(coords,
             by = "country_code") %>% 
  mutate(year = as.numeric(year),
         percentage = round(percentage, 2)) 

```

```{r, eval = FALSE}
# leaflet map

labor_leaflet <- labor_tidy_coords %>% 
  filter(year == "2019") %>% 
  slice(1:169) %>% 
  st_as_sf() 


palette <- colorBin(palette = "viridis",
                    domain = labor_leaflet$percentage,
                    bins = 5,
                    na.color ="transparent",
                    reverse = TRUE)

content <- paste("Country:", labor_leaflet$country_name, 
                 "<br> Year:", labor_leaflet$year, 
                 "<br> Percentage:", labor_leaflet$percentage)

text <- paste("Country: ", labor_leaflet$country_name,
              "<br>",
              "Female labor force: ", paste(labor_leaflet$percentage, "%", sep = "")) %>%
  lapply(htmltools::HTML)



labor_leaflet %>% 
  leaflet() %>%
  setView(lat = 0, lng = 0, zoom = 1) %>%
  addTiles() %>%
  addPolygons(
    fillColor = ~ palette(percentage),
    weight = 0.5,
    opacity = 1,
    color = "white",
    smoothFactor = 0.2,
    fillOpacity = 1,
    label = text,
    highlight = highlightOptions(
      color = "#666",
      weight = 2,
      bringToFront = TRUE,
      opacity = 1)
    ) %>%
    addLegend(
      pal = palette,
      values = labor_leaflet$percentage,
      opacity = 0.7,
      title = paste("Female labor force 2019",
                    "<br>",
                    "%"),
      position = "bottomleft"
      ) 

```

```{r, eval = FALSE}
# leaflet shiny app

labor_shiny <- labor_tidy_coords %>% 
  slice(1:5070) %>% 
  st_as_sf() 


ui <- fluidPage(
  sliderInput("range",
              "year",
              min = min(labor_shiny$year),
              max = max(labor_shiny$year),
              value = min(labor_shiny$year),
              step = 1),
  leafletOutput("labormap")
)


server <- function(input, output, session) {

output$labormap <- renderLeaflet({
labor_shiny %>% 
  filter(year == input$range) %>%
  leaflet() %>%
  setView(lat = 0, lng = 0, zoom = 1) %>%
  addTiles() %>%
  addPolygons(
    fillColor = ~ palette(percentage),
    weight = 0.5,
    opacity = 1,
    color = "white",
    smoothFactor = 0.2,
    fillOpacity = 1,
    label = text,
    highlight = highlightOptions(
      color = "#666",
      weight = 2,
      bringToFront = TRUE,
      opacity = 1)
    ) %>%
    addLegend(
      pal = palette,
      values = labor_shiny$percentage,
      opacity = 0.7,
      title = paste("Female labor force 2019",
                    "<br>",
                    "%"),
      position = "bottomleft"
      ) 
})

}

shinyApp(ui, server)

```

## Employment

```{r, eval = FALSE}
# world development indicators from world bank https://datacatalog.worldbank.org/search/dataset/0037712
wdi <- read.csv(here("data/WDIData.csv"))
```

```{r, eval = FALSE}
employment <- wdi %>% 
  filter(Indicator.Name %in% c("Employment to population ratio, 15+, female (%) (modeled ILO estimate)",
                               "Employment to population ratio, 15+, male (%) (modeled ILO estimate)",
                               "Employment to population ratio, ages 15-24, female (%) (modeled ILO estimate)",
                               "Employment to population ratio, ages 15-24, female (%) (national estimate)"))
```




# Women in Law

```{r}
wbl_df <- read_xlsx(here("data/WBL50YearPanelDetailsWeb21Feb2021.xlsx"), sheet = 2) # https://wbl.worldbank.org/en/wbl-data

indicators <- read.csv(here("data/API_17_DS2_en_csv_v2_3371618.csv"), skip = 4)
```

## WBL index

The WBL (The Women Business and the Law Index) index measures the economic empowerment of women. It is based on the countries' formal laws and regulations that have a bearing on women's economic participation, covering eight areas such as parenthood, equality of pay. It tracks how laws affect women at different stages in their working lives and focusing on those laws applicable in the main business city [@civilsdaily]

### WBL index over time

```{r}
# faceted choropleth map
wbl_index_map <- wbl_df %>% 
  select(economy, wbcodev2, reportyr, `WBL INDEX`)


## get geometry for each country
data("World")

coords <- World %>% 
  select("iso_a3",
         "name",
         "geometry") %>% 
  rename(wbcodev2 = "iso_a3")


## join spatial df with wbl_df
wbl_index_map <- wbl_index_map %>% 
  left_join(coords,
            by = "wbcodev2") %>% 
  drop_na() %>% 
  st_as_sf() 


## add tooltip
wbl_index_map$tooltip <- 
  glue_data(wbl_index_map,
            "Country: {economy}",
            "\nPercentage: {`WBL INDEX`}")


## create choropleth map
ggplotly(
  

wbl_index_map %>%
  filter(reportyr %in% c(2012:2021)) %>% 
  ggplot() +
  geom_sf(aes(geometry = geometry,
              fill = `WBL INDEX`,
              text = tooltip),
          color = "white",
          size = 0.1) +
  facet_wrap(vars(reportyr),
             ncol = 3) +
  scale_fill_viridis_c(direction = -1) +
  theme_map() +
  theme(strip.text = element_text(colour = "black"),
        strip.background = element_rect(fill ="white", colour = "white"),
        plot.caption = element_text(hjust = 0)) +
  labs(fill = "WBL index"),
tooltip = "text"

) %>% 
  layout(legend = list(orientation = "h")) %>% ## not working?????
  config(displayModeBar = FALSE,
         displaylogo = FALSE) 


```

```{r, eval = FALSE}
# WIP!!!

# fig <- wbl_index_map %>%
#   plot_ly(frame = ~reportyr, 
#           type ='choropleth', 
#           locations = wbl_index_map$economy,   
#           z = wbl_index_map$`WBL INDEX`, 
#             # zmin = 0,
#             # zmax = 500000,
#           text = wbl_index_map$economy, 
#           color = ~`WBL INDEX`,
#           colorscale = "Electric") %>%
#   layout(
#     geo = list(scope = "world"),
#          title = "Number of confirmed cases of New Coronary Pneumonia in Asia")
# fig


# ggplotly(
#   
# 
# wbl_index_map %>%
#   ggplot() +
#   geom_sf(aes(geometry = geometry,
#               fill = `WBL INDEX`,
#               text = tooltip,
#               frame = reportyr),
#           color = "white",
#           size = 0.1) +
#   # geom_polygon(aes(frame = reportyr),
#   #              color = "white", 
#   #              size = 0.1) +
#   # facet_wrap(vars(reportyr),
#   #            ncol = 3) +
#   scale_fill_viridis_c(direction = -1) +
#   theme_map() +
#   theme(strip.text = element_text(colour = "black"),
#         strip.background = element_rect(fill ="white", colour = "white"),
#         plot.caption = element_text(hjust = 0)) +
#   labs(fill = "WBL index"),
# tooltip = "text"
# 
# ) %>% 
#   config(displayModeBar = FALSE,
#          displaylogo = FALSE) %>% 
#   animation_slider(currentvalue = list(prefix = "Year", 
#                                        font = list(color = "orange")))

```


```{r, eval=FALSE}
# shiny app for WBL index

shinyApp(
  
ui <- fluidPage(
  sliderInput("range",
              "year",
              min = min(wbl_index_map$reportyr),
              max = max(wbl_index_map$reportyr),
              value = min(wbl_index_map$reportyr),
              step = 1,
              sep = ""),
  leafletOutput("wblmap")
),


server <- function(input, output, session) {
  
  map_years <- reactive({
    wbl_index_map_year <- wbl_index_map %>%
      filter(reportyr == input$range)

  })

output$wblmap <- renderLeaflet({
  
  palette <- colorBin(palette = "viridis",
                      domain = map_years()$`WBL INDEX`,
                      bins = 5,
                      na.color ="transparent",
                      reverse = TRUE)

  text <- paste("Country:", map_years()$economy, 
              "<br> Year:", map_years()$reportyr, 
              "<br> WBL index:", map_years()$`WBL INDEX`) %>%
  lapply(htmltools::HTML)
  
  
 map_years() %>%
    leaflet() %>%
    setView(lat = 30, lng = 0, zoom = 1) %>%
    addTiles() %>%
    addPolygons(
      fillColor = ~ palette(map_years()$`WBL INDEX`),
      weight = 0.5,
      opacity = 1,
      color = "white",
      smoothFactor = 0.2,
      fillOpacity = 1,
      label = text,
    highlight = highlightOptions(
      color = "#666",
      weight = 2,
      bringToFront = TRUE,
      opacity = 1)
    ) %>%
    addLegend(
      pal = palette,
      values = map_years()$`WBL INDEX`,
      opacity = 0.7,
      title = "WBL Index",
      position = "bottomleft"
      ) 
})

},

  options = list(height = 500)
)

# shinyApp(ui, server)

```

### Avergae score of WBL indicators by region and year

```{r}
wbl_indicators <- wbl_df %>% 
  select("economy",
         "Region",
         "Income group",
         "reportyr",
         "MOBILITY",
         "WORKPLACE",
         "PAY",
         "MARRIAGE",
         "PARENTHOOD",
         "ENTREPRENEURSHIP",
         "ASSETS",
         "PENSION") %>% 
         # "Can a woman apply for a passport in the same way as a man?",
         # "Can a woman travel outside the country in the same way as a man?",
         # "Can a woman travel outside her home in the same way as a man?",
         # "Can a woman choose where to live in the same way as a man?") %>% 
  pivot_longer(cols = 5:12,
               names_to = "indicator",
               values_to = "score") 
```


```{r, fig.width=8}
wbl_indicators_avg <- wbl_indicators  %>% 
  filter(reportyr %in% c(2000:2021)) %>% 
  group_by(Region,
           reportyr,
           indicator) %>% 
  summarise_at(vars(score), 
               list(avg_score = mean)) %>% 
  mutate(avg_score = round(avg_score, 2))



wbl_indicators_avg$tooltip <- 
  glue_data(wbl_indicators_avg,
            "Region: {Region}",
            "\nYear: {reportyr}",
            "\nAverage score: {avg_score}")


# plot it
ggplotly(
  
wbl_indicators_avg %>% 
  ggplot(aes(x = reportyr,
             y = avg_score,
             group = Region,
             color = Region)) +
  geom_line(aes(text = tooltip),
            size = 0.3) +
  geom_point(aes(text = tooltip),
             size = 0.1) +
  facet_wrap(vars(indicator),
             ncol = 4) +
  scale_color_brewer(palette = "Paired") +
  scale_x_continuous(breaks = seq(2000, 2021, by = 1)) +
  theme_light() +
  theme(axis.text.x = element_text(angle = 90, size = 6),
        axis.text.y = element_text(size = 6),
        # axis.line = element_line(colour = "black"),
        strip.text = element_text(size = 8,
                                  face = "bold",
                                  colour = "black"),
        strip.background = element_rect(fill ="white", colour = "white"),
        legend.text = element_text(size = 8),
        panel.grid.major.x = element_blank()) +
        # panel.border = element_blank()) +
  labs(x = NULL,
       y = NULL,
       title = "Average score of WBL indicators by region and year",
       color = NULL),
  tooltip = "text"
  
) %>% 
  layout(annotations = list(x = 0.1, 
                            y = -0.3, 
                            text = "Source: World Bank",
                            showarrow = FALSE, 
                            xref = "paper", 
                            yref = "paper",
                            xanchor = "right", 
                            yanchor = "auto", 
                            xshift = 0, 
                            yshift = 0,
                            font = list(size = 8)),
         legend = list(orientation = "h") 
         ) %>% 
  config(displayModeBar = FALSE,
         displaylogo = FALSE) 
  
```
### Mobility 

```{r}
mob_df <- wbl_df %>%
  select("economy",
         "Region",
         "Income group",
         "reportyr",
         "MOBILITY",
         "Can a woman apply for a passport in the same way as a man?",
         "Can a woman travel outside the country in the same way as a man?",
         "Can a woman travel outside her home in the same way as a man?",
         "Can a woman choose where to live in the same way as a man?") %>%
  pivot_longer(cols = 6:9,
               names_to = "question",
               values_to = "answer")

```

```{r}
# calculate mean mobility index by income group and year
# mob_avg <- mob_df %>% 
#   filter(reportyr %in% c(2000:2021)) %>% 
#   group_by(Region,
#            reportyr) %>% 
#   summarise_at(vars(MOBILITY), 
#                list(mobility = mean)) 
# 
# 
# 
# mob_avg$tooltip <- 
#   glue_data(mob_avg,
#             "Region: {Region}",
#             "\nYear: {reportyr}",
#             "\nMobility score: {mobility}")
# 
# 
# # plot it
# ggplotly(
#   
# mob_avg %>% 
#   ggplot(aes(x = reportyr,
#              y = mobility,
#              group = Region,
#              color = Region)) +
#   geom_line(aes(text = tooltip)) +
#   geom_point(aes(text = tooltip),
#              size = 0.7) +
#   scale_color_brewer(palette = "Paired") +
#   scale_x_continuous(breaks = seq(2000, 2021, by = 1)) +
#   theme_light() +
#   theme(axis.text.x = element_text(angle = 90, size = 8),
#         panel.grid.major.x = element_blank()) +
#   labs(x = NULL,
#        y = "Average mobility score",
#        title = "Mobility score by regions and year",
#        color = NULL),
#   tooltip = "text"
#   
# ) %>% 
#   layout(annotations = list(x = 0.1, 
#                             y = -0.15, 
#                             text = "Source: World Bank",
#                             showarrow = FALSE, 
#                             xref = "paper", 
#                             yref = "paper",
#                             xanchor = "right", 
#                             yanchor = "auto", 
#                             xshift = 0, 
#                             yshift = 0,
#                             font = list(size = 8)
# )) %>% 
#   config(displayModeBar = FALSE,
#          displaylogo = FALSE) 

```



```{r, fig.width=8}
ggplotly(

mob_df %>%
  filter(answer == "Yes",
         reportyr %in% c("1971", "2021")) %>%
  group_by(Region,
           reportyr,
           question) %>%
  summarise(count = n()) %>%
  ggplot(aes(x = reportyr,
             y = count,
             group = Region,
             color =  Region)) +
  geom_line() +
  geom_point(size = 0.8) +
  facet_wrap(vars(question),
             scales = "free",
             labeller = label_wrap_gen(width = 53)) +
  scale_color_brewer(palette = "Paired") +
  scale_x_continuous(breaks = seq(1971, 2021,  by = 50)) +
  theme_light() +
  theme(panel.grid.minor.x = element_blank(),
        panel.border = element_blank(),
        strip.text = element_text(colour = "black"),
        strip.background = element_rect(fill ="white", colour = "white"),
        strip.text.x = element_text(size = 7),
        plot.title = element_text(size = 14))+
  labs(x = NULL,
       y = "Number of countries",
       color = NULL,
       title = "Mobility scored questions answered with a 'yes' "),
tooltip = "count"

) %>%
    layout(annotations = list(x = 0.1,
                              y = -0.15,
                              text = "Source: World Bank",
                              showarrow = FALSE,
                              xref = "paper",
                              yref = "paper",
                              xanchor = "right",
                              yanchor = "auto",
                              xshift = 0,
                              yshift = 0,
                              font = list(size = 8)
          # title = list(text = "Mobility scored questions answered with a 'yes' ", y = 0.99),
)) %>%
  config(displayModeBar = FALSE,
         displaylogo = FALSE)



```

### Workplace

```{r read-data}
workplace <- read_xlsx(here("data/WBL50YearPanelDetailsWeb21Feb2021.xlsx"), sheet = 5, range = "A2:Q192") 
```

```{r}
workplace_long <- workplace %>% 
  pivot_longer(cols = c(3, 6, 9, 12),
               names_to = "question",
               values_to = "answer") 

workplace_long %>% 
  filter(answer == "No") %>% 
  select("EconomyName",
         "question",
         "answer") %>% 
  group_by(question) %>% 
  summarise(count = n()) %>% 
  mutate(question = fct_reorder(question, count)) %>% 
  ggplot(aes(x = question,
             y = count,
             fill = question)) +
  geom_col() +
  coord_flip() +
  scale_x_discrete(labels = c("Is there legislation on sexual harassment \nin employment",
                            "Does the law prohibit discrimination \nin employment base on gender",
                            "Can a woman get a job in \nthe same way as a man",
                            "Are there criminal penalties or civil \nremidies for sexual harassment \nin employment")) +
  scale_y_continuous(limits = c(0, 60)) +
  scale_fill_brewer(palette = "Blues") +
  theme_light() +
  theme(panel.grid.major.x = element_blank(),
        legend.position = "none") +
  labs(x = NULL,
       y = "Number of countries",
       title = "Workplace scored questions answered with a 'No' in 2021")
  
  
  
  # theme(panel.grid.minor.y = element_blank(),
  #       legend.position = "none") 
  




```

### Gender gap index VS WBL index

```{r}
gap <- read_csv(here("data/gender_gap_index.csv"))
# https://tcdata360.worldbank.org/indicators/af52ebe9?country=BRA&indicator=27959&viz=line_chart&years=2006,2021
```

```{r}
gap %>% 
  filter(Indicator == "Overall Global Gender Gap Index",
         `Subindicator Type` == "Index") %>% 
  select(`Country Name`,
         "2021") %>% 
  rename(gender_gap_index = "2021",
         economy = `Country Name`) %>% 
  right_join(wbl_df,
             by = "economy") %>% 
  filter(reportyr == "2021") %>% 
  select(economy,
         reportyr,
         Region,
         `Income group`,
         `WBL INDEX`,
         gender_gap_index) %>% 
  filter(!is.na(gender_gap_index)) %>% 
  ggplot(aes(x = `WBL INDEX`,
             y = gender_gap_index)) +
  geom_point() +
  geom_smooth(method = lm) +
  scale_x_continuous(limits = c(25, 100)) +
  stat_cor(aes(label = ..r.label..)) +
  theme_light()
  
```








```{r}
# pivot longer world bank gdp data 
# gdp_region <- gdp %>% 
#   select(-c(`Country Code`,
#             `Indicator Name`,
#             `Indicator Code`,
#             `...66`)) %>% 
#   pivot_longer(cols = 2:62,
#                names_to = "year",
#                values_to = "gdp_per_capita") %>% 
#   rename(country_name = `Country Name`) %>% 
#   left_join(wbl_region,
#             by = "country_name") %>% 
#   filter(!is.na(Region))
#   
#   
# wbl_df %>% 
#   select(economy,
#          Region,
#          reportyr,
#          `WBL INDEX`) %>% 
#   pivot_wider(names_from = reportyr,
#               values_from = `WBL INDEX`)
```






## Proportion of seats held by women in national parliaments

```{r}
# cleaning
seats <- indicators %>% 
  filter(Indicator.Name == "Proportion of seats held by women in national parliaments (%)",
         Country.Name %in% c("Africa",
                             "East Asia & Pacific",
                             "Europe & Central Asia",
                             "Latin America & the Caribbean",
                             "Middle East & North Africa",
                             "South Asia")) %>% 
  select(-Indicator.Code) %>% 
  pivot_longer(cols = 4:65,
               names_to = "year",
               values_to = "percentage") %>% 
  mutate(year = str_remove(year, "X"),
         percentage = round(percentage, 2)) %>% 
  filter(!is.na(percentage))

```


```{r, fig.width=8}
# plot it

seats$tooltip <- 
  glue_data(seats,
            "Region: {Country.Name}",
            "\nYear: {year}",
            "\nPercentage: {paste0(seats$percentage, '%', sep = '')}")

ggplotly(
  
  seats %>% 
  ggplot(aes(x = year,
             y = percentage,
             group = Country.Name,
             color = Country.Name)) +
  geom_line(aes(text = tooltip)) +
  geom_point(aes(text = tooltip),
             size = 0.7) +
  scale_color_brewer(palette = "Set1") +
  scale_y_continuous(breaks = seq(0, 30, by = 5)) +
  theme_light() +
  theme(axis.text.x = element_text(angle = 90, size = 8),
        panel.grid.major.x = element_blank()) +
  labs(x = NULL,
       y = "Percentage %",
       title = "Proportion of seats held by women in national parliaments (%)",
       color = "Regions"),
  tooltip = "text"
  
) %>% 
  layout(annotations = list(x = 0.1, 
                            y = -0.15, 
                            text = "Source: World Bank",
                            showarrow = FALSE, 
                            xref = "paper", 
                            yref = "paper",
                            xanchor = "right", 
                            yanchor = "auto", 
                            xshift = 0, 
                            yshift = 0,
                            font = list(size = 8)
)) %>% 
  config(displayModeBar = FALSE,
         displaylogo = FALSE) 
  
```



`



## Suffrage (V-Dem data)

```{r}
dem <- readRDS(here("data/V-Dem-CY-Full+Others-v11.1.rds"))
# https://www.v-dem.net/vdemds.html
```


```{r, eval = FALSE}
# extract regions from wbl workbank data
wbl_region <- wbl_df %>% 
  select(economy, Region) %>% 
  distinct() %>% 
  rename("country_name" = "economy")

# jonin region data with v-dem data
suffrage_restricted <- dem %>% 
  select(country_name,
         year,
         v2elfemrst) %>% 
  filter(year %in% c(1990:2020),
         v2elfemrst %in% c(0, 1)) %>% 
  drop_na() %>% 
  left_join(wbl_region,
            by = "country_name") 
  
```

```{r}
# no suffrage
suffrage_restricted %>% 
  pivot_wider(names_from = v2elfemrst,
              values_from = v2elfemrst) %>% 
  select(country_name,
         year, 
         Region, 
         "0") %>% 
  rename("No female suffrage" = "0",
         Country = country_name,
         Year = year) %>% 
  drop_na("No female suffrage") %>%
  arrange(Year) %>% 
  select(Country,
         Year,
         Region) %>% 
  relocate(Year, .before = Country) %>% 
  gt() %>% 
  cols_width(Country ~ px(80),
             Region ~ px(250)) %>% 
  tab_header(title = md("**Countries with no female suffrage**"))




# restricted suffrage 
suffrage_restricted %>% 
  pivot_wider(names_from = v2elfemrst,
              values_from = v2elfemrst) %>% 
  select(country_name,
         year, 
         Region, 
         "1") %>% 
  rename("Restriced female suffrage" = "1",
         Country = country_name,
         Year = year) %>% 
  drop_na() %>% 
  arrange(Year) %>% 
  select(Country,
         Year,
         Region) %>% 
  relocate(Year, .before = Country) %>% 
  gt() %>% 
  cols_width(Country ~ px(250),
             Region ~ px(250)) %>% 
  tab_header(title = md("**Countries with restricted female suffrage**"))
  

```





```


# Reference





